### 2024-01-03 documentation/thesis/thesis_document.tex
more thesis

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \textbf{Ready to use hardware sensor designs}
\item
  \textbf{Taking automatic measurements from sensors}
\item
  \textbf{Ready to use data analysis functions}
\item
  \textbf{Open storage formats for data export}
\item
  \textbf{Easy software configuration}
\item
  \textbf{User expandable data processing pipelines}
\end{enumerate}

@@

The main aim of this project is to develop a low-cost Hall sensor
interface that is also universally expandable. The focus is on mapping
different sensors and being compatible with different magnet types and
shapes. This ensures broad applicability in different scenarios. Another
goal is reproducibility to ensure consistent results. Easy communication
with standard PC hardware maximises the user-friendliness of the
interface. The flexibility to support different sensors and magnets
makes the system versatile and opens up possibilities for different
applications. A low-cost Hall sensor interface will therefore not only
be economically attractive, but also facilitate the integration of Hall
sensors in different contexts. In addition, the low-cost Hall sensor
interface will serve as a development platform for the data evaluation
\gls{mrp} library and provide real measurement data from magnets. In
addition, the interface firmware creates a basis for the development of
a data protocol for exchanging measured values. This makes it easy to
integrate your own measuring devices into the \gls{mrp} ecosystem at a
later date. This is only possible with a minimal functional hardware and
firmware setup and was developed for this purpose first.

>>>>

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \textbf{Ready to use hardware sensor designs} A universal,
  easy-to-integrate Hall sensor design allows users to evaluate the
  framework quickly and cost-effectively. The pre-built hardware sensors
  provide an optimal solution for research, reducing development time
  and achieving repeatable measurement results. Once successfully
  evaluated, the Hall sensor design should be easily adaptable to other
  sensors without the need for major firmware changes.
\item
  \textbf{Taking automatic measurements from sensors} The purpose of the
  framework is to enable the automated acquisition of measurement data
  from various connected hadware sensors. The user should be able to
  configure various measurement series, which should then be carried out
  by the framework without further user interaction.
\item
  \textbf{Open storage formats for data export} The use of open storage
  formats for the export of data enables an interoperable data exchange
  environment. The implementation of standardized formats improves the
  portability and long-term availability of data. This encourages the
  exchange and further processing of measurement data in other software
  tools.
\item
  \textbf{Ready to integrate data analysis functions} Once it is
  possible to record and store measured values, it should be possible
  for the user to analyse and visualize this data using various
  algorithms. The focus here should be on extending the framework with
  user-created algorithms.
\item
  \textbf{User programmable data processing pipelines} User-programmable
  data processing pipelines enable the flexible design of data
  processing sequences by users. The framework should enable users to
  create their own Anylse pipelines with the previously defined data
  analysis functions.
\end{enumerate}

@@

A defined main objective of this project is the development of a
cost-effective Hall sensor interface that is also universally
expandable. The focus is on mapping different sensors and being
compatible with different magnet types and shapes. This ensures broad
applicability in different scenarios. Another goal is reproducibility to
ensure consistent results. Easy communication with standard PC hardware
maximises the user-friendliness of the interface. The flexibility to
support different sensors and magnets makes the system versatile and
opens up possibilities for different applications. A low-cost Hall
sensor interface will therefore not only be economically attractive, but
also facilitate the integration of Hall sensors in different contexts.
In addition, the low-cost Hall sensor interface will serve as a
development platform for the data evaluation \gls{mrp} library and
provide real measurement data from magnets. In addition, the interface
firmware creates a basis for the development of a data protocol for
exchanging measured values. This makes it easy to integrate your own
measuring devices into the \gls{mrp} ecosystem at a later date. This is
only possible with a minimal functional hardware and firmware setup and
was developed for this purpose first.
